---
title: "IFM2"
author: "Mai Nguyen"
date: "2024-04-16"
output:
  word_document: default
  html_document: default
---

Install package vrtest

Step 1: Import data of KDC stock and define time series

```{r}

kdc <-KDC$price_KDC[1:475]
dt <- diff(log(kdc))
length(dt)
```
Step 2: Test for the validity of Lo-MacKinlay model
In this step, we will check whether the KDC log-return series satify the Lo - Mackinlay model by Lo&MacKinlay Variance Ratio test.

Lo & McKinley Variance Ratio Test
- H0: The time series is a random walk, sigma^2(r_t(k))= k*sigma^2(r_t)
- H1: The time series is not a random walk
By M-statistic, we will derive the results of this test. According to Lo&MacKinlay,
(giai thich)

```{r}
kvec <- c(2,4,8,16)

Lo.Mac(dt,kvec)

```
Conclusion: 
- q=2. reject H0 => there is autocorrelation at t-1
- q=4  not reject H0 => there is not autocorrelation at t-3
- q=8 reject H0 => there is autocorrelation at t =7
=> KDC log-return series do not satisfy AR(1)
=> Lo&MacKinlay Model does not satisfy.

To further proof the conclusion above, we plot the ACF and PACF of the KDC log-return series.

PACF and ACF of the log-return series
```{r}
acf(dt)

```
Final conclusion


